---
title: "The *ComplexDiff* user's guide"
author: |
  | Mingxiang Teng <mxteng@jimmy.harvard.edu>
  | Rafael A. Irizarry <rafa@jimmy.harvard.edu>
  | Department of Biostatistics, Dana-Farber Cancer Institute &
  | Harvard T.H. Chan School of Public Health, Boston, MA, USA
date: "`r Sys.Date()`"
output:
  BiocStyle::pdf_document:
    toc: true
bibliography: ComplexDiff.bib
graphics: yes
vignette: >
  %\VignetteIndexEntry{The ComplexDiff user's guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignettePackage{ComplexDiff}
  %\VignetteEncoding{UTF-8}
---

```{r para, echo = FALSE, results='hide'}
BiocStyle::markdown()
knitr::opts_chunk$set(dev="png",fig.show="hold",
               fig.width=8,fig.height=4.5,fig.align="center",
               message=FALSE,collapse=TRUE)
set.seed(1)
```

# Introduction

Comparing protein binding differences between biological conditions can be
accomplished 


# Getting Started

Load the package in R

```{r library}
library(ComplexDiff)
```

# Preparing Inputs


# Differential Binding Regions

For  algorithms details, please refer to our manuscript [@teng].

## Count reads for genomic regions


## Determine protein binding type


## Estimate normalization size factors


## Identify differential binding regions


## Optional permutation analysis


# Summary


# References
